### 2020-03-18 paper.tex
Template

%%
%% This is file `sample-sigchi.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigchi')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigchi.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigchi]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigchi]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{The 1907 Franklin Model D roadster.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
{\bfseries also} include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed {\itshape below} the figure.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, an article in a proceedings (of a conference,
  symposium, workshop for example) (paginated proceedings article)
  \cite{Andler79}, a proceedings article with all possible elements
  \cite{Smith10}, an example of an enumerated proceedings article
  \cite{VanGundy07}, an informally published work \cite{Harel78},
  a couple of preprints \cite{Bornmann2019, AnzarootPBM14},
  a doctoral dissertation \cite{Clarkson85}, a master's thesis:
  \cite{anisi03}, an online document / world wide web resource
  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
  (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigchi.tex'.

### 2020-03-18 paper.tex
More stuff

@@
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+\author{Michael James}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
+  \institution{University of California, San Diego}
 }
+\email{m3james@eng.ucsd.edu}
 
-\author{Lars Th{\o}rv{\"a}ld}
+\author{John Renner }
 \affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
+  \institution{University of California, San Diego}
 }
-
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
-
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
-
-\author{John Smith}
-\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{\institution{The Kumquat Consortium}}
-\email{jpkumquat@consortium.net}
+\email{jmrenner@eng.ucsd.edu}
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+    Abstracts are scary.
 \end{abstract}
@@
 \url{https://www.acm.org/publications/proceedings-template}.
+
+\section{Method}
+% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
+% Explain your study design, illustrate how the study's results will provide
+% evidence for/against your hypothesis, and how the question, hypothesis, and
+% study all line up. We encourage you to mirror/copy/adapt other researchers
+% methods (e.g. by drawing from the class readings) whenever appropriate (and
+% not when it isn't appropriate).
+
+% There are three major points you should hit here.
+
+% Study design:
+% What are you going to do? Be detailed and precise.
+
+% Measures:
+% How will you know you succeeded? What will you measure? How will you measure
+% it? What might your results look like?
+
+% Ecological Validity:
+% Why does your study answer your research question? Why
+% does your evaluation address your hypothesis? Make sure your study, and the
+% variables you're measuring, properly address the question you are asking.
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=\textwidth]{results/task_points.png}
+  \caption{
+    Examples did not noticeably affect time-to-completion, except in Task 2
+    where the effect is dramatic.
+  }
+  \label{fig:data-points}
+\end{figure*}
+
+\section{Results}
+% Figures.
+% Analysis
+\section{Discussion}
 

### 2020-03-18 results/gen.py

@@ -1,0 +1,70 @@
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.ticker as ticker
+
+with open('results.csv') as csvfile:
+    reader = csv.DictReader(csvfile)
+    data = [dict(row) for row in reader]
+    for d in data:
+        del d['']
+
+print(data)
+
+def duration_to_sec(dur):
+    mins_as_sec = int(f"{dur[0]}{dur[1]}") * 60
+    secs = float("".join(dur[3:]))
+    return mins_as_sec + secs
+
+def dur_fmt(secs, _):
+    return "{:02}:{:02}".format(int(secs/60), int(secs % 60))
+
+task_keys = [f"Task {i}" for i in range(1,5)]
+rank_keys = [f"Rank {i}" for i in range(1,5)]
+# Assign ranks
+for i, t in enumerate(task_keys):
+    for rank, row in enumerate(sorted(data, key=lambda row: row[t])):
+        row[rank_keys[i]] = rank + 1
+
+example_ranks = [row[r] for r in rank_keys for row in data if row["Variant"] == "Examples"]
+baseline_ranks = [row[r] for r in rank_keys for row in data if row["Variant"] == "No Examples"]
+
+print(example_ranks, len(example_ranks), sum(example_ranks))
+print(baseline_ranks, len(baseline_ranks), sum(baseline_ranks))
+
+
+example_tasks = [[duration_to_sec(row[t]) for row in data if row["Variant"] == "Examples"] for t in task_keys]
+baseline_tasks = [[duration_to_sec(row[t]) for row in data if row["Variant"] == "No Examples"] for t in task_keys]
+
+print(example_tasks)
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Fixing random state for reproducibility
+np.random.seed(19680801)
+
+# fake up some data
+spread = np.random.rand(50) * 100
+center = np.ones(25) * 50
+flier_high = np.random.rand(10) * 100 + 100
+flier_low = np.random.rand(10) * -100
+
+
+fig1, axs = plt.subplots(ncols=len(example_tasks))
+axs[0].set_ylabel("Time (mm:ss)")
+for task_i in range(len(task_keys)):
+    example_tasks = [duration_to_sec(row[task_keys[task_i]]) for row in data if row["Variant"] == "Examples"]
[…]

### 2020-03-18 paper.tex
More figs
Some stuff in methods

@@
-%%
-%% This is file `sample-sigchi.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigchi')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-sigchi.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
+\RequirePackage[hyphens]{url}
 \documentclass[sigchi]{acmart}
+%% Include the standard set of goodies
+\include{builtins/std}
 
@@
 % variables you're measuring, properly address the question you are asking.
+\subsection{Measures}
+% We expected to see that examples increased the speed of candidate selection
+% with little to no loss in accuracy.
+% %
+% Furthermore we expected that speedup to be explained by decreased reliance on
+% the interpreter.
+% %
+% Specifically, users should no longer need to run their own input-output tests
+% on the candidate programs.
+
+For each participant, we measured:
+\begin{itemize}
+    \item Time-to-correct solution (per task)
+    \item Count of incorrect guesses (per task)
+    \item Count and type of interpreter queries (across all tasks)
+\end{itemize}
+
+The first metric directly tests the hypothesis that examples improve
+selection speed, but the result could be misleading if there was also a
+change in selection accuracy.
+%
+Counting incorrect guesses ensures that any such change is captured.
+%
+Beyond assessing the effectiveness of examples, measuring how often and why
+participants used the interactive interpreter provides insight into any 
+behavior changes that might occur.
+
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{method/control-ui.png}
+        \caption{Control treatment, no examples}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{method/treatment-ui.png}
+        \caption{Experimental treatment, examples}
+    \end{subfigure}
+    \caption{Each participant received one of the two treatments for the duration of the study.}
+\end{figure*}
+
+\section{Results}
+% Figures.
 \begin{figure*}[ht]
@@
 \end{figure*}
-
-\section{Results}
-% Figures.
 % Analysis

### 2020-03-18 paper.tex
Some changes

@@
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
+\section{Method}
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\section{Method}
 % --- COPIED FROM ABSTRACT ASSIGNMENT --- %
@@
 
-% Measures:
-% How will you know you succeeded? What will you measure? How will you measure
-% it? What might your results look like?
-
 % Ecological Validity:
@@
 \subsection{Measures}
-% We expected to see that examples increased the speed of candidate selection
-% with little to no loss in accuracy.
-% %
-% Furthermore we expected that speedup to be explained by decreased reliance on
-% the interpreter.
-% %
-% Specifically, users should no longer need to run their own input-output tests
-% on the candidate programs.
-
 For each participant, we measured:

### 2020-03-18 paper.tex
Some stuff on results

@@
 
-\author{John Renner }
+\author{John Renner}
 \affiliation{%
@@
 \section{Results}
+\subsection{Time-to-correct solution}
+Cumulatively, across the four tasks, we did not observe a significant change
+in the time-to-correct solution.
+%
+A Wilcoxon Rank-Sum test, performed on the aggregate of per-task rankings,
+yielded a confidence interval $p=0.14$.
+%
+Performing rank-sum of ranks is an especially conservative test, because it weighs 
+per-task rankings equally, regardless of the absolute times.
+
+Although the results do not indicate a change across the board, our data shows a dramatic
+speedup for the example group in Task 2 (see Figure~\ref{fig:data-points}).
+%
+This may indicate that certain tasks benefit from examples while others do not.
+%
+We discuss this more thoroughly in Section~\ref{sec:discussion}
+
+\subsection{Incorrect guesses}
+\subsection{Interpreter usage}
 % Figures.
@@
 \section{Discussion}
-
+\label{sec:discussion}
 \subsection{Template Styles}

### 2020-03-19 abstract.tex
break apart into sections -- i think this makes it easier to parallelize

--- 2020-03-18 paper.tex
@@
-\RequirePackage[hyphens]{url}
-\documentclass[sigchi]{acmart}
-%% Include the standard set of goodies
-\include{builtins/std}
-
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
-
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title is Hope}
-
-\author{Michael James}
-\affiliation{%
-  \institution{University of California, San Diego}
-}
-\email{m3james@eng.ucsd.edu}
-
-\author{John Renner }
-\affiliation{%
-  \institution{University of California, San Diego}
-}
-\email{jmrenner@eng.ucsd.edu}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
 \begin{abstract}
@@
 \end{abstract}
-
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-
-\section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
-
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
-
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
-\section{Method}
-
-% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
-% Explain your study design, illustrate how the study's results will provide
-% evidence for/against your hypothesis, and how the question, hypothesis, and
-% study all line up. We encourage you to mirror/copy/adapt other researchers
-% methods (e.g. by drawing from the class readings) whenever appropriate (and
-% not when it isn't appropriate).
-
-% There are three major points you should hit here.
-
-% Study design:
-% What are you going to do? Be detailed and precise.
-
-% Ecological Validity:
-% Why does your study answer your research question? Why
-% does your evaluation address your hypothesis? Make sure your study, and the
-% variables you're measuring, properly address the question you are asking.
-\subsection{Measures}
-For each participant, we measured:
-\begin{itemize}
-    \item Time-to-correct solution (per task)
-    \item Count of incorrect guesses (per task)
-    \item Count and type of interpreter queries (across all tasks)
-\end{itemize}
-
-The first metric directly tests the hypothesis that examples improve
-selection speed, but the result could be misleading if there was also a
-change in selection accuracy.
-%
-Counting incorrect guesses ensures that any such change is captured.
-%
-Beyond assessing the effectiveness of examples, measuring how often and why
-participants used the interactive interpreter provides insight into any 
-behavior changes that might occur.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{method/control-ui.png}
-        \caption{Control treatment, no examples}
-    \end{subfigure}%
-    ~ 
-    \begin{subfigure}[t]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{method/treatment-ui.png}
-        \caption{Experimental treatment, examples}
-    \end{subfigure}
-    \caption{Each participant received one of the two treatments for the duration of the study.}
-\end{figure*}
-
-\section{Results}
-% Figures.
-\begin{figure*}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{results/task_points.png}
-  \caption{
-    Examples did not noticeably affect time-to-completion, except in Task 2
-    where the effect is dramatic.
-  }
-  \label{fig:data-points}
-\end{figure*}
-% Analysis
-\section{Discussion}
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigchi]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78},
-  a couple of preprints \cite{Bornmann2019, AnzarootPBM14},
-  a doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{bib}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
-\end{document}
-\endinput
-%%
-%% End of file `sample-sigchi.tex'.

### 2020-03-19 methods.tex
break apart into sections -- i think this makes it easier to parallelize

--- 2020-03-18 paper.tex
@@
-\RequirePackage[hyphens]{url}
-\documentclass[sigchi]{acmart}
-%% Include the standard set of goodies
-\include{builtins/std}
-
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
-
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title is Hope}
-
-\author{Michael James}
-\affiliation{%
-  \institution{University of California, San Diego}
-}
-\email{m3james@eng.ucsd.edu}
-
-\author{John Renner }
-\affiliation{%
-  \institution{University of California, San Diego}
-}
-\email{jmrenner@eng.ucsd.edu}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
-\begin{abstract}
-    Abstracts are scary.
-\end{abstract}
-
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-
-\section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
-
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
-
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
 \section{Method}
@@
 \end{figure*}
-
-\section{Results}
-% Figures.
-\begin{figure*}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{results/task_points.png}
-  \caption{
-    Examples did not noticeably affect time-to-completion, except in Task 2
-    where the effect is dramatic.
-  }
-  \label{fig:data-points}
-\end{figure*}
-% Analysis
-\section{Discussion}
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigchi]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78},
-  a couple of preprints \cite{Bornmann2019, AnzarootPBM14},
-  a doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{bib}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
-\end{document}
-\endinput
-%%
-%% End of file `sample-sigchi.tex'.

### 2020-03-19 paper.tex
break apart into sections -- i think this makes it easier to parallelize

--- 2020-03-18 paper.tex
@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
+% \setcopyright{acmcopyright}
+% \copyrightyear{2018}
+% \acmYear{2018}
+% \acmDOI{10.1145/1122445.1122456}
 
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+% \acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
+%   Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
+% \acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+%   June 03--05, 2018, Woodstock, NY}
+% \acmPrice{15.00}
+% \acmISBN{978-1-4503-XXXX-X/18/06}
 
@@
 %% article.
-\begin{abstract}
-    Abstracts are scary.
-\end{abstract}
+\input{abstract}
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+% \ccsdesc[500]{Computer systems organization~Embedded systems}
+% \ccsdesc[300]{Computer systems organization~Redundancy}
+% \ccsdesc{Computer systems organization~Robotics}
+% \ccsdesc[100]{Networks~Network reliability}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+% \keywords{datasets, neural networks, gaze detection, text tagging}
 
@@
 \maketitle
+\input{intro}
 
-\section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
+\input{methods}
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+\input{results}
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
-\section{Method}
-
-% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
-% Explain your study design, illustrate how the study's results will provide
-% evidence for/against your hypothesis, and how the question, hypothesis, and
-% study all line up. We encourage you to mirror/copy/adapt other researchers
-% methods (e.g. by drawing from the class readings) whenever appropriate (and
-% not when it isn't appropriate).
-
-% There are three major points you should hit here.
-
-% Study design:
-% What are you going to do? Be detailed and precise.
-
-% Ecological Validity:
-% Why does your study answer your research question? Why
-% does your evaluation address your hypothesis? Make sure your study, and the
-% variables you're measuring, properly address the question you are asking.
-\subsection{Measures}
-For each participant, we measured:
-\begin{itemize}
-    \item Time-to-correct solution (per task)
-    \item Count of incorrect guesses (per task)
-    \item Count and type of interpreter queries (across all tasks)
-\end{itemize}
-
-The first metric directly tests the hypothesis that examples improve
-selection speed, but the result could be misleading if there was also a
-change in selection accuracy.
-%
-Counting incorrect guesses ensures that any such change is captured.
-%
-Beyond assessing the effectiveness of examples, measuring how often and why
-participants used the interactive interpreter provides insight into any 
-behavior changes that might occur.
-
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{method/control-ui.png}
-        \caption{Control treatment, no examples}
-    \end{subfigure}%
-    ~ 
-    \begin{subfigure}[t]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{method/treatment-ui.png}
-        \caption{Experimental treatment, examples}
-    \end{subfigure}
-    \caption{Each participant received one of the two treatments for the duration of the study.}
-\end{figure*}
-
-\section{Results}
-% Figures.
-\begin{figure*}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{results/task_points.png}
-  \caption{
-    Examples did not noticeably affect time-to-completion, except in Task 2
-    where the effect is dramatic.
-  }
-  \label{fig:data-points}
-\end{figure*}
-% Analysis
-\section{Discussion}
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigchi]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{The 1907 Franklin Model D roadster.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-{\bfseries also} include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed {\itshape below} the figure.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, an article in a proceedings (of a conference,
-  symposium, workshop for example) (paginated proceedings article)
-  \cite{Andler79}, a proceedings article with all possible elements
-  \cite{Smith10}, an example of an enumerated proceedings article
-  \cite{VanGundy07}, an informally published work \cite{Harel78},
-  a couple of preprints \cite{Bornmann2019, AnzarootPBM14},
-  a doctoral dissertation \cite{Clarkson85}, a master's thesis:
-  \cite{anisi03}, an online document / world wide web resource
-  \cite{Thornburg01, Ablamowicz07, Poker06}, a video game (Case 1)
-  \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05} and
-  (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
+\input{discussion}
 
@@
 
-\section{Research Methods}
-
-\subsection{Part One}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
 \end{document}

### 2020-03-19 results.tex
break apart into sections -- i think this makes it easier to parallelize

\section{Results}
\subsection{Time-to-correct solution}
Cumulatively, across the four tasks, we did not observe a significant change
in the time-to-correct solution.
%
A Wilcoxon Rank-Sum test, performed on the aggregate of per-task rankings,
yielded a confidence interval $p=0.14$.
%
Performing rank-sum of ranks is an especially conservative test, because it weighs
per-task rankings equally, regardless of the absolute times.

Although the results do not indicate a change across the board, our data shows a dramatic
speedup for the example group in Task 2 (see Figure~\ref{fig:data-points}).
%
This may indicate that certain tasks benefit from examples while others do not.
%
We discuss this more thoroughly in Section~\ref{sec:discussion}

\subsection{Incorrect guesses}
\subsection{Interpreter usage}
% Figures.
\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{results/task_points.png}
  \caption{
    Examples did not noticeably affect time-to-completion, except in Task 2
    where the effect is dramatic.
  }
  \label{fig:data-points}
\end{figure*}

### 2020-03-19 intro.tex
Updated Intro; first BAD pass

\section{Introduction}

Imagine asking your computer to write a function for you and it works on the
first try.
%
Well, program synthesis isn't quite there.
%
But getting there will necessarily involve some back and forth between the user
and computer.
%
Often the function specification is less precise the than function requested.
%
In this case, a program synthesizer can come up with any number of solutions
that all meet the specification, to varying degrees of utility.

Our work is based on\textsc{Hoogle+}, a program synthesis engine for the
Haskell programming language \cite{hoogle_plus_2020}.
%
A user inputs a type signature of a function, like \texttt{a -> [Maybe a] -> a}
(read: ``A function that takes a thing and a list of optional-things, and
returns a thing'').
%
\textsc{Hoogle+} then looks for Haskell programs that use library calls (from
a small, builtin set of functions) that satisfies the type signature.
%
Note that there may be an infinite number of so-called \emph{inhabitants} of a type.
%
This presents a search problem for users of the system.

How can a user sift through the programs synthesized to find the right
implementation of the type signature, for their use case?
%
We extend the system to provide some input-output examples for a chosen set of
queries, enough to run our study.
%
For now these examples were stubbed and chosen without particular regard for how
they might distinguish various candidate solutions.
%

### 2020-03-19 methods.tex
Added trials subsection

@@
 
+\subsection{Trials}
+We had two variants.
+%
+The control version of the tool only showed programs that matched a type signature.
+%
+The treatment version showed three input-output examples with each program
+suggested by the synthesizer.
+
+Each participant went through one training task and four trial tasks.
+%
+The task was to find the best implementation of a type signature and a
+description of what the program should do.
+%
+Timing began as soon as they were handed a card containing the task, and ended
+when they pointed out the correct solution.
+%
+There was one correct answer per task---and task 3 had no correct solution.
+%
+Each participant was in a single variant for the entirety of their tasks.
+
 \begin{figure*}[t!]

### 2020-03-19 discussion.tex
Task 2 light discussion; future work created

\section{Discussion}
\label{sec:discussion}

\subsection{Statistical insignificance}
Why it be like it do?

\subsection{Task 2}
The Wilcoxon Rank-Sum test on task 2 was $p=0.03$, showing a runaway success
that examples do help participants find the correct program faster.
%
We suspect that second task was unique among the four participants completed.
%
The tool produced up to ten candidate programs for a given type signature, and
for task 2, the correct solution was at the very end.
%
Task 1 and 4 had the correct solution listed in the first and second places,
respectively.

### 2020-03-19 future.tex
Task 2 light discussion; future work created

\section{Future Work}
\label{sec:future}

F U T U R E

### 2020-03-19 results.tex
Some more results

@@
 
-\subsection{Incorrect guesses}
+\subsection{Incorrect selections}
+When participants made an incorrect selection, they were allowed to keep
+selecting until they found the correct program.
+%
+This happened 3 times in the \noexamples group and 5 times in the example group.
+%
+In the example group, a single participant made 3 incorrect guesses on a
+single task.
+%
+This participant was also the only one who ranked their Haskell knowledge as a 1 out of 5.
+%
+Futhermore, the incorrect selections contained incorrect input/output pairs. 
+%
+With these anomalies in mind, we don't believe this study has determined a definitive answer
+on the relationship between examples and error rates.
+
 \subsection{Interpreter usage}
+In the \noexamples group, participants made a median of 6 type queries,
+executed 3 subexpressions, and ran 3 full candidates across all 4 tasks.
+%
+In the \examples group, however, participants made a median of 0 queries of any kind.
+%
+It's clear that, introducing examples reduced participants reliance on the
+interpreter to gather information.
+
 % Figures.

### 2020-03-19 conclusion.tex
added conclusion

\section{Conclusion}

We have shown an experimental setup to suss out when input-output examples help
users in a type-directed synthesis environment.
%
Overall our results did not show a statistical significance ($p = 0.14$);
however, we did find some interesting data points for further research.
%
Specifically, one task did conclude a statistically significant result ($p =
0.03$), Task 2.
%
We offered a theory explaining it and future experiments that could falsify our
claim.
%
We found that users did rely on an interpreter more in the absence of examples
to offer a "feel" for the candidate programs.

### 2020-03-19 discussion.tex
Clean up task 2 stuff

@@
 
-\subsection{Statistical insignificance}
-Why it be like it do?
-
-\subsection{Task 2}
-The Wilcoxon Rank-Sum test on task 2 was $p=0.03$, showing a runaway success
-that examples do help participants find the correct program faster.
+\subsection{Hope for examples}
+Although the study failed to show that examples aided candidate selection in
+the general case, it's possible that in specific case it makes a large difference.
 %
-We suspect that second task was unique among the four participants completed.
+A Wilcoxon Rank-Sum test on the data from Task 2 shows that the \example
+group was faster with a confidence of $p=0.03$.
 %
-The tool produced up to ten candidate programs for a given type signature, and
-for task 2, the correct solution was at the very end.
+While this could just be noise, the correct solution for Task 2 was 10th in
+the list while Tasks 1 and 2 had their solution in the first two spots.
 %
-Task 1 and 4 had the correct solution listed in the first and second places,
-respectively.
+Task 3 had no solution.
+%
+If examples speed up candidate assessment, we'd expect this effect to be
+magnified by the number of candidates assessed.
+%
+Because users had to sift through 9 incorrect solutions to get to the correct
+one, it makes sense that Task 2 showed the most dramatic effect.
+%
+A study that randomizes solution location rather than preserving the synthesizer's ordering
+could test this hypothesis.

### 2020-03-19 future.tex

@@
 
-F U T U R E
+\subsection{Methodology changes}
+After encountering only one participant with minimal Haskell knowledge it became
+clear we needed to randomize the treatment for each task.
+%
+This would mitigate the effects of outliers on any one variant, distributing
+their effect on each treatment.
+%
+
+\subsection{Future Directions}
+This work touches on but does not seek to evaluate whether recognition of a
+correct solution or recall of necessary parts of a correct solution are more
+useful in this type-directed search setting.
+%
+In our \noexamples group, participants largely relied on the interpreter to tell
+them what different parts of a candidate solution were doing.
+%
+In effect, they used the interpreter as a source of documentation.
+%
+So, it remains to be seen what kinds of tasks users accomplish faster with
+documentation as an aid vs input-output examples.
+%

### 2020-03-19 abstract.tex
abstract and methods update

@@
 \begin{abstract}
-    Abstracts are scary.
+Program synthesis has been focusing on making newer and better tools; however,
+few have evaluated how people like to interact with them and what features users
+find useful.
+%
+We evaluate the addition of examples to type directed program synthesis.
+%
+We measured 10 participants between two variants, each with 4 tasks.
+%
+We do not find a statistical significance, in general, with the addition of
+examples.
+%
+We do note, that one task did have a significant difference in performance
+between groups.
+%
+Further evaluation is needed to determine a reason for this.
 \end{abstract}

### 2020-03-19 methods.tex
consistency is key
abstract and methods update

@@
 \subsection{Measures}
+We gathered 10 participants from around our department's building and from the
+local Hillcrest community.
+%
+We required that participants be able to read some Haskell code.
+
 For each participant, we measured:
@@
     \item Time-to-correct solution (per task)
-    \item Count of incorrect guesses (per task)
+    \item Count of incorrect selections (per task)
     \item Count and type of interpreter queries (across all tasks)

### 2020-03-19 discussion.tex
MOOOORE

@@
 %
-A Wilcoxon Rank-Sum test on the data from Task 2 shows that the \example
+A Wilcoxon Rank-Sum test on the data from Task 2 shows that the \examples
 group was faster with a confidence of $p=0.03$.
@@
 could test this hypothesis.
+
+\subsection{Task-treatment vs. Participant-treatment}
+For this study, participants were assigned to either the \examples or
+\noexamples group.
+%
+This had the benefit of being simple to implement, and easy to understand for
+participants, but was not without drawbacks.
+%
+The current study is sensitive to varying levels of Haskell knowledge, relying on
+the law of large numbers to eventually even things out.
+%
+Unfortunately, this study only contained 10 participants, and so is skewed by
+the particulars of each participants skill levels.
+%
+We opted for the simpler study due to constraints for class, but a future
+study might be better served by giving each participant a randomized mix of \examples
+and \noexamples treatments.

### 2020-03-19 future.tex
whoops duplicates

--- 2020-03-19 future.tex
@@
 
-F U T U R E
+This work touches on but does not seek to evaluate whether recognition of a
+correct solution or recall of necessary parts of a correct solution are more
+useful in this type-directed search setting.
+%
+In our \noexamples group, participants largely relied on the interpreter to tell
+them what different parts of a candidate solution were doing.
+%
+In effect, they used the interpreter as a source of documentation.
+%
+So, it remains to be seen what kinds of tasks users accomplish faster with
+documentation as an aid vs input-output examples.
+%

### 2020-03-19 intro.tex
We have a methods section

@@
 
-Our work is based on\textsc{Hoogle+}, a program synthesis engine for the
+Our work is based on \hoogleplus, a program synthesis engine for the
 Haskell programming language \cite{hoogle_plus_2020}.
@@
 %
-\textsc{Hoogle+} then looks for Haskell programs that use library calls (from
+\hoogleplus then looks for Haskell programs that use library calls (from
 a small, builtin set of functions) that satisfies the type signature.

### 2020-03-19 methods.tex
We have a methods section

--- 2020-03-19 methods.tex
@@
 \section{Method}
-
-% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
-% Explain your study design, illustrate how the study's results will provide
-% evidence for/against your hypothesis, and how the question, hypothesis, and
-% study all line up. We encourage you to mirror/copy/adapt other researchers
-% methods (e.g. by drawing from the class readings) whenever appropriate (and
-% not when it isn't appropriate).
-
-% There are three major points you should hit here.
-
-% Study design:
-% What are you going to do? Be detailed and precise.
-
-% Ecological Validity:
-% Why does your study answer your research question? Why
-% does your evaluation address your hypothesis? Make sure your study, and the
-% variables you're measuring, properly address the question you are asking.
-\subsection{Measures}
-For each participant, we measured:
-\begin{itemize}
-    \item Time-to-correct solution (per task)
-    \item Count of incorrect guesses (per task)
-    \item Count and type of interpreter queries (across all tasks)
-\end{itemize}
-
-The first metric directly tests the hypothesis that examples improve
-selection speed, but the result could be misleading if there was also a
-change in selection accuracy.
-%
-Counting incorrect guesses ensures that any such change is captured.
-%
-Beyond assessing the effectiveness of examples, measuring how often and why
-participants used the interactive interpreter provides insight into any
-behavior changes that might occur.
-
 \begin{figure*}[t!]
@@
     \caption{Each participant received one of the two treatments for the duration of the study.}
+    \label{fig:ui}
 \end{figure*}
+To assess whether examples aid recognition of candidate programs, we
+developed two variants of a synthesizer interface (see Figure~\ref{fig:ui})
+
+\paragraph{No-examples variant}
+%
+In the \noexamples variant, a user can enter a Haskell type signature at the top and get a
+list of 10 candidate programs back.
+%
+These candidates are unmodified and in the same order that \hoogleplus
+synthesizer generates them.
+%
+The results are deterministic meaning that for a given type signature, the
+response is always the same.
+
+\paragraph{Examples variant}
+The \examples variant extends the \noexamples variant with input/output
+examples for each candidate.
+%
+For each, type signature in the study, we manually created three simple
+inputs of the appropriate type.
+%
+Each candidate program received the same three inputs.
+
+\subsection{Procedure}
+We gathered 10 haskell-literate participants from around our department's
+building and from the local Hillcrest community.
+%
+Participants were each assigned to either the \noexamples treatment or the
+\examples treatment for the duration of the study.
+%
+Each participant was presented a laptop with their respective tool variant open
+and an interactive haskell interpreter (GHCI) open to the side.
+%
+Throughout the study participants were allowed to use only the tool and the
+interpreter.
+
+After a brief tutorial tasks, participants were asked to complete 4 tasks.
+%
+Each task consisted of a type signature they would enter, and an informal
+english description of the behavior they were looking for.
+%
+They would then enter the type signature and identify the candidate program that
+met the specification, if it was present.
+%
+Participants were told at the beginning that the solution may not be present
+in the list---Task 3 did not have a solution in the list.
+
+After completing the four tasks, the candidates were given a brief survey
+that asked them about their haskell experience, their opinions on the tool,
+and their strategies for finding the correct answer.
+
+\subsection{Measures}
+
+For each participant, we measured:
+\begin{itemize}
+    \item Time-to-correct solution (per task)
+    \item Count of incorrect selections (per task)
+    \item Count and type of interpreter queries (across all tasks)
+\end{itemize}
+
+The first metric directly tests the hypothesis that examples improve
+selection speed, but the result could be misleading if there was also a
+change in selection accuracy.
+%
+Counting incorrect guesses ensures that any such change is captured.
+%
+Beyond assessing the effectiveness of examples, measuring how often and why
+participants used the interactive interpreter provides insight into any
+behavior changes that might occur.

### 2020-03-20 conclusion.tex
grammar fixes

@@
 Specifically, one task did conclude a statistically significant result ($p =
-0.03$), Task 2.
+0.03$), Task~2.
 %
@@
 We found that users did rely on an interpreter more in the absence of examples
-to offer a "feel" for the candidate programs.
+to offer a "feel" for the candidate programs and to lookup documentation.
+%
+We believe our study was sufficiently underpowered to be unable to make a
+definitive claim on the overall utility of examples in a type-directed synthesis
+environment.

### 2020-03-20 discussion.tex
grammar fixes

@@
 Although the study failed to show that examples aided candidate selection in
-the general case, it's possible that in specific case it makes a large difference.
+the general case, it's possible that in specific cases examples makes a large difference.
 %

### 2020-03-20 intro.tex
grammar fixes

@@
 
-Imagine asking your computer to write a function for you and it works on the
-first try.
+Program Synthesis works by taking a specification and generating a program that
+implements the specification.
 %
-Well, program synthesis isn't quite there.
+In a sense it is the holy grail of computer science.
 %
-But getting there will necessarily involve some back and forth between the user
-and computer.
+There is a plethora of work trying to go straight to the goal.
 %
-Often the function specification is less precise the than function requested.
+Some use input-output examples as their specification
+\cite{Feser_Chaudhuri_Dillig_2015}.
 %
-In this case, a program synthesizer can come up with any number of solutions
-that all meet the specification, to varying degrees of utility.
+Others use types and examples \cite{Osera_Zdancewic_2015}.
+%
+Still others use just types \cite{hoogle_plus_2020}.
 
-Our work is based on \hoogleplus, a program synthesis engine for the
+However, in lieu of waiting for some graduate student to solve this field, we
+adopt a more practical approach and want to bring existing techniques to users.
+%
+In doing so, we seek to help users understand the solutions that program
+synthesizers come up with.
+%
+Since current specifications tend to be underpowered, many unhelpful programs
+come up from synthesizers.
+%
+
+Specifically, we seek to understand the degree to which input-output examples,
+as properties of synthesized functions (instead of as specifications), aid users
+in finding the program they came to the synthesizer for.
+
+We base our work on \hoogleplus, a program synthesis engine for the
 Haskell programming language \cite{hoogle_plus_2020}.
@@
 %
-Note that there may be an infinite number of so-called \emph{inhabitants} of a type.
+Note that there may be an infinite number of candidate solutions that satisfy a type.
 %

### 2020-03-20 methods.tex
grammar fixes

@@
 %
-These candidates are unmodified and in the same order that \hoogleplus
-synthesizer generates them.
+These candidates are mostly unmodified and in the same order that \hoogleplus
+generates them.
+%
+The sole exception is Task 2, where the correct answer was manually inserted at
+the end of the existing candidates.
 %
@@
 %
-For each, type signature in the study, we manually created three simple
+For each type signature in the study, we manually created three simple
 inputs of the appropriate type.
@@
 \subsection{Procedure}
-We gathered 10 haskell-literate participants from around our department's
+We gathered 10 Haskell-literate participants from around our department's
 building and from the local Hillcrest community.
@@
 Each participant was presented a laptop with their respective tool variant open
-and an interactive haskell interpreter (GHCI) open to the side.
+and an interactive Haskell interpreter (GHCI) open to the side.
 %
@@
 
-After a brief tutorial tasks, participants were asked to complete 4 tasks.
+After a brief tutorial task, participants were asked to complete 4 tasks.
 %
-Each task consisted of a type signature they would enter, and an informal
+Each task consisted of a type signature and an informal
 english description of the behavior they were looking for.
@@
 After completing the four tasks, the candidates were given a brief survey
-that asked them about their haskell experience, their opinions on the tool,
+that asked them about their Haskell experience, their opinions on the tool,
 and their strategies for finding the correct answer.

### 2020-03-20 results.tex
We have a methods section
grammar fixes

@@
 \section{Results}
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=\textwidth]{results/task_points.png}
+  \caption{
+    Examples did not noticeably affect time-to-completion, except in Task 2
+    where the effect is dramatic.
+  }
+  \label{fig:data-points}
+\end{figure*}
 \subsection{Time-to-correct solution}
@@
 A Wilcoxon Rank-Sum test, performed on the aggregate of per-task rankings,
-yielded a confidence interval $p=0.14$.
+yielded a confidence interval of $p=0.14$.
 %
 Performing rank-sum of ranks is an especially conservative test, because it weighs
-per-task rankings equally, regardless of the absolute times.
+per-task rankings equally, regardless of the absolute times or relative
+difficulty of tasks.
 
@@
 %
-Futhermore, the incorrect selections contained incorrect input/output pairs. 
+Furthermore, the incorrect selections contained incorrect input/output pairs.
 %
@@
 % Figures.
-\begin{figure*}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{results/task_points.png}
-  \caption{
-    Examples did not noticeably affect time-to-completion, except in Task 2
-    where the effect is dramatic.
-  }
-  \label{fig:data-points}
-\end{figure*}

### 2020-03-20 intro.tex
edit pass

@@
 
-Program Synthesis works by taking a specification and generating a program that
+Program synthesis works by taking a specification and generating a program that
 implements the specification.
 %
-In a sense it is the holy grail of computer science.
+In a sense it is the holy grail of computer science--to write a program for you.
 %
-There is a plethora of work trying to go straight to the goal.
+There is a plethora of work trying to go straight to the goal, in a variety of ways.
 %
@@
 
-However, in lieu of waiting for some graduate student to solve this field, we
+However, in lieu of waiting for some graduate student to solve this open
+problem, we
 adopt a more practical approach and want to bring existing techniques to users.
 %
-In doing so, we seek to help users understand the solutions that program
+In doing so, we seek to help users understand the solutions that current program
 synthesizers come up with.
@@
 
-Specifically, we seek to understand the degree to which input-output examples,
-as properties of synthesized functions (instead of as specifications), aid users
+Specifically, we seek to understand the degree to which input-output examples on
+synthesized functions aid users
 in finding the program they came to the synthesizer for.
@@
 A user inputs a type signature of a function, like \texttt{a -> [Maybe a] -> a}
-(read: ``A function that takes a thing and a list of optional-things, and
+(read: ``A function that takes a thing and a list of optional-things, then
 returns a thing'').
@@
 \hoogleplus then looks for Haskell programs that use library calls (from
-a small, builtin set of functions) that satisfies the type signature.
+a small, builtin set of functions) that satisfy the type signature.
 %

### 2020-03-20 intro.tex
Oops, I rewrote the intro

--- 2020-03-19 intro.tex
@@
 \section{Introduction}
+Writing code is difficult and often inadvisable. 
+%
+A recent approach to this classic conundrum is \emph{program synthesis} which
+takes a specification and generates a program that implements the
+specification---saving us from ourselves by letting the computer do the work.
+%
+The specification may be a collection of input/output pairs
+\cite{Feser_Chaudhuri_Dillig_2015}, a type signature \cite{hoogle_plus_2020},
+or even a combination of the two \cite{Osera_Zdancewic_2015}.
+%
+These specifications are intentionally vague; many programs different
+programs might meet the specification.
+%
+This keeps specification easy, but it requires the synthesizer to either guess,
+or, more realistically, produce multiple candidate programs.
 
-Imagine asking your computer to write a function for you and it works on the
-first try.
+Sifting through a list of candidate programs can be timeconsuming, so much so
+that it might be faster to write the code yourself.
 %
-Well, program synthesis isn't quite there.
+If we could speed up this process, without requiring more input from the
+user, we could allow programmers to both write easy specifications and
+efficiently find their desired program.
+
+In this work, we evaluate whether automatically generated input-output examples
+for candidate programs will speed up the selection process.
 %
-But getting there will necessarily involve some back and forth between the user
-and computer.
+We asked users to complete a series of synthesis tasks using a modified
+version of, \hoogleplus, a program synthesizer for the Haskell
+\cite{hoogle_plus_2020}, that produces input/output examples.
 %
-Often the function specification is less precise the than function requested.
-%
-In this case, a program synthesizer can come up with any number of solutions
-that all meet the specification, to varying degrees of utility.
-
-Our work is based on \hoogleplus, a program synthesis engine for the
-Haskell programming language \cite{hoogle_plus_2020}.
-%
-A user inputs a type signature of a function, like \texttt{a -> [Maybe a] -> a}
-(read: ``A function that takes a thing and a list of optional-things, and
-returns a thing'').
-%
-\hoogleplus then looks for Haskell programs that use library calls (from
-a small, builtin set of functions) that satisfies the type signature.
-%
-Note that there may be an infinite number of so-called \emph{inhabitants} of a type.
-%
-This presents a search problem for users of the system.
-
-How can a user sift through the programs synthesized to find the right
-implementation of the type signature, for their use case?
-%
-We extend the system to provide some input-output examples for a chosen set of
-queries, enough to run our study.
-%
-For now these examples were stubbed and chosen without particular regard for how
-they might distinguish various candidate solutions.
-%
+We find that while input/output examples do not appear to provide consisten
+speedups, there is likely a set of circumstances where the speedup is
+dramatic.

### 2020-03-20 intro.tex
typo changes

@@
 Writing code is difficult and often inadvisable.
+
+A recent approach to this classic conundrum is \emph{program synthesis} which
+takes a specification and generates a program that implements it---saving us
+from ourselves by letting the computer do hard part.
 %
-A recent approach to this classic conundrum is \emph{program synthesis} which
-takes a specification and generates a program that implements the
-specification---saving us from ourselves by letting the computer do the work.
-%
-The specification may be a collection of input/output pairs
+A specification may be a collection of input/output pairs
 \cite{Feser_Chaudhuri_Dillig_2015}, a type signature \cite{hoogle_plus_2020},
@@
 %
-These specifications are intentionally vague; many programs different
-programs might meet the specification.
+These specifications are intentionally vague; many different
+programs might meet the same specification.
 %
-This keeps specification easy, but it requires the synthesizer to either guess,
+While this keeps specification simple, it requires the synthesizer to either guess,
 or, more realistically, produce multiple candidate programs.
 
-Sifting through a list of candidate programs can be timeconsuming, so much so
+Sifting through a list of candidate programs can be time-consuming, so much so
 that it might be faster to write the code yourself.
@@
 If we could speed up this process, without requiring more input from the
-user, we could allow programmers to both write easy specifications and
+user, we could allow programmers to both write simple specifications and
 efficiently find their desired program.
@@
 %
-We find that while input/output examples do not appear to provide consisten
+We find that while input/output examples do not appear to provide consistent
 speedups, there is likely a set of circumstances where the speedup is

### 2020-03-20 abstract.tex
update abstract

@@
 \begin{abstract}
-Program synthesis has been focusing on making newer and better tools; however,
-few have evaluated how people like to interact with them and what features users
-find useful.
+Program synthesis takes the hard work out of \emph{writing} code, at the cost of
+having to \emph{read} more code to decipher the best program for a given
+situation.
+%
+This shifts the problem of writing code to reading new, unfamiliar code.
 %
